\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Deterministic build settings
\pdfinfo{
  /CreationDate (D:19700101000000Z)
  /ModDate (D:19700101000000Z)
  /Creator (pdflatex)
  /Producer (pdflatex)
}
\pdftrailerid{}
\pdfsuppressptexinfo15

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Saurabh Shubham} \\ \vspace{1pt}
    \small +49-1705452439 $|$ \href{mailto:saurabh.friday@gmail.com}{\underline{saurabh.friday@gmail.com}} $|$ 
    \href{https://linkedin.com/in/saurabh-shubham/}{\underline{linkedin.com/in/saurabh-shubham}} $|$
    \href{https://github.com/Saurabh3333}{\underline{github.com/Saurabh3333}} $|$
    \href{https://saurabh3333.github.io}{\underline{saurabh3333.github.io}}
\end{center}

\section{Summary}
Data Engineer with 5+ years of experience building and optimizing data pipelines, ETL/ELT workflows, and backend services. Skilled in modern data platforms including Dagster, Airflow, and dbt. Proven ability to streamline operations, improve reliability, and design scalable infrastructure for large-scale and real-time processing.

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {GROPYUS}{Berlin, Germany}
      {Data Engineer}{Aug 2022 -- Present}
      \resumeItemListStart
        \resumeItem{Designed and optimized data pipelines for KUKA robots enabling real-time production insights.}
        \resumeItem{Streamlined data flows between robotic systems and enterprise platforms, improving automation efficiency.}
        \resumeItem{Orchestrated data operations and transformations leveraging Dagster, Airflow, dbt, and DLT on Azure.}
      \resumeItemListEnd

    \resumeSubheading
      {Sigmoid}{Bengaluru, India}
      {Software Development Engineer}{Jun 2021 -- Jul 2022}
      \resumeItemListStart
        \resumeItem{Built and maintained ETL pipelines for processing large-scale sales data from Colgate-Walmart.}
        \resumeItem{Automated reporting and analytics for EVR, CBR, and Net Sales data, improving data availability.}
        \resumeItem{Developed infrastructure and processing flows using Python, PySpark, Pandas, Terraform, and Airflow on GCP and AWS.}
      \resumeItemListEnd

    \resumeSubheading
      {Amdocs}{Pune, India}
      {Software Engineer}{Jun 2019 -- Jun 2021}
      \resumeItemListStart
        \resumeItem{Developed and delivered core backend features for Comcast CRM using Java, Spring, and REST/SOAP APIs.}
        \resumeItem{Automated internal process tracking and business needs workflows, enhancing operational tracking.}
        \resumeItem{Led design, wireframing, and implementation of new integration modules.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Apparel Recommendation System}{TensorFlow, Keras}
      {Machine Learning System}{}
      \resumeItemListStart
        \resumeItem{Developed a product recommender using machine learning techniques to personalize user experiences.}
      \resumeItemListEnd
    \resumeSubheading
      {Alexa IPL Skill}{Node.js, PostgreSQL}
      {Voice Application}{}
      \resumeItemListStart
        \resumeItem{Created a voice application capable of answering queries related to IPL match data.}
      \resumeItemListEnd
    \resumeSubheading
      {Quality Assessment Chrome Extension}{Google Inception V3}
      {Content Verification Tool}{}
      \resumeItemListStart
        \resumeItem{Built an extension for real-time content authenticity checking using an Inception V3 model.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, Java, JavaScript, C++} \\
     \textbf{Data Tools}{: Airflow, Dagster, dbt, DLT, PySpark, Pandas} \\
     \textbf{Cloud \& Infrastructure}{: Azure, AWS, Google Cloud (GCP), Terraform} \\
     \textbf{Databases}{: PostgreSQL, MySQL, MongoDB} \\
     \textbf{Other}{: REST APIs, Git, Unix/Linux}
    }}
 \end{itemize}

\section{Achievements}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Awards \& Recognition}{2018}
      {}{}
      \resumeItemListStart
        \resumeItem{Facebook PyTorch Challenge Scholarship.}
        \resumeItem{Top 200 ranking in Infosys HackWithInfy coding competition.}
        \resumeItem{Invitee to Google Tech Intern Connect.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}
